### 2022-05-27 doc/VerticalArrangements.tex
fixed bug in code that was erroenously eliminated vertical markets. Fixed bug in code that was not properly zeoring out elements for upstream integrated products. Added figures depicting profitibility across bargaining parameters and number of integrated firms. added figure comparing outcomes across models.

For each combination of number of retailers, number of wholesalers, number of incumbent integrated firms, and bargaining parameter, we draw 1,000 different sets of market primitives.  After eliminating situations where the merger is unprofitable to the merging firms, as well as markets that do not pass the Hypothetical Monopolist Test, we have 2.7 million markets remaining.\footnote{The Hypothetical Monopolist Test is a market definition exercise that checks whether a monopolist that owns all products in a candidate market would raise the price of at least one of the merging producers' products by at least a ``small but significant non-transitory increase in price'' (SSNIP), which we take to be 5\%. } Each market treats as primitives the number of retailers, the number of wholesalers, the bargaining parameter, and the wholesaler and retailer marginal costs.

@@

The median average wholesale pre-merger price is \$4.50, and the median average retail pre-merger price is \$13.  Recall that the market size is set to 1, meaning that average price is equal to total pre-merger expenditures.  Pre-merger HHIs range from 2,814 at the $25^{th}$ percentile to 5,030 at the $75^{th}$, with a median of 3,703. HHIs for vertical mergers increase by 1,298 points at the median, resulting in a median post-merger HHI equal to 5,995.\footnote{We compute the post-merger HHI for vertical mergers by treating the merged firms' market share as the sum of all the shares of downstream products that either use the upstream partner's input or are sold by the downstream partner.  }  HHIs for downstream mergers increase by 2,015 points at the median, resulting in a median post-merger HHI equal to 4,914.  HHIs for upstream mergers increase by 2,063 points at the median, resulting in a median post-merger HHI equal to 5,238. HHIs for integrated mergers increase by 2,770 points at the median, resulting in a median post-merger HHI equal to 7,280.

>>>>

For each combination of number of retailers, number of wholesalers, number of incumbent integrated firms, and bargaining parameter, we draw 1,000 different sets of market primitives.  After eliminating situations where the merger is unprofitable to the merging firms, as well as markets that do not pass the Hypothetical Monopolist Test, we have 1.6 million markets remaining.\footnote{The Hypothetical Monopolist Test is a market definition exercise that checks whether a monopolist that owns all products in a candidate market would raise the price of at least one of the merging producers' products by at least a ``small but significant non-transitory increase in price'' (SSNIP), which we take to be 5\%. } Each market treats as primitives the number of retailers, the number of wholesalers, the bargaining parameter, and the wholesaler and retailer marginal costs.

@@

The median average wholesale pre-merger price is \$4.50, and the median average retail pre-merger price is \$13.  Recall that the market size is set to 1, meaning that average price is equal to total pre-merger expenditures.  Pre-merger HHIs range from 2,923 at the $25^{th}$ percentile to 4,966 at the $75^{th}$, with a median of 3,742. HHIs for vertical mergers increase by 1,298 points at the median, resulting in a median post-merger HHI equal to 5,995.\footnote{We compute the post-merger HHI for vertical mergers by treating the merged firms' market share as the sum of all the shares of downstream products that either use the upstream partner's input or are sold by the downstream partner.  }  HHIs for downstream mergers increase by 2,015 points at the median, resulting in a median post-merger HHI equal to 4,914.  HHIs for upstream mergers increase by 2,063 points at the median, resulting in a median post-merger HHI equal to 5,238. HHIs for integrated mergers increase by 2,770 points at the median, resulting in a median post-merger HHI equal to 7,280.
